---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/"
)
options(width=100)
library(utsMultivariate)
```

### Introduction

This package provides S3 classes ("uts_vector" and "uts_matrix") for multivariate unevenly spaced time series.

R users familiar with vectors and matrices should find it straightforward to work with the corresponding time series objects, because the usage of many functions (such as [, [[, length, etc.) is completely analogous.


### Installation

This package is not yet available on CRAN, but can be installled from GitHub, either using the `R` package [devtools](https://cran.r-project.org/web/packages/devtools/index.html):

```{r, eval=FALSE}
devtools::install_github("andreas50/uts", build_vignettes=TRUE)
devtools::install_github("andreas50/utsMultivariate")
```

or using the `R` package [remotes](https://cran.r-project.org/web/packages/remotes/index.html):

```{r, eval=FALSE}
remotes::install_github("andreas50/uts")
remotes::install_github("andreas50/utsMultivariate")
```

### Sample Code

```{r}
# Get sample unevenly-spaced time series vector
x <- ex_uts_vector()
x
```
